---
title: "Overview of gameday"
author: "Rebecca Johnston"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of gameday}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## Introduction to gameday

Get key NHL hockey info.

When living in Canada, you must:

* Live hockey;
* Breathe hockey;
* Think about hockey all the time;

Or:
 
* Be banished from civilization and inevitably perish in the tundra.

This package helps you to:
 
* Prevent your banishment by providing basic hockey stats so you can masquerade as a hockey lover. Go Canucks! Or whatever that Vancouver hockey team is called...

In particular, this package has two functions:

1. `gday()`
2. `scores`

```{r, include=FALSE}
library("gday")
```

## Check gameday of a team with `gday()`
The function `gday()` returns TRUE if the specified NHL team plays on a specified date and FALSE otherwise. The first argument is the name of an NHL team (as a chracter string, i.e. in quotes), and the second argument is the date of the game, as "YYYY-MM-DD".

For example, to check if the Toronto Maple Leafs played on November 9th, 2014 using `gday()`:

```{r}
gday(team = "Maple Leafs", date = "2014-11-09")

# or simply

gday("Maple Leafs", "2014-11-09")
```

Notes: 

* If no arguments are specified in `gday()`, the default `team` is "Canucks" and the default `date` is today's date.
* The case in argument `team` is ignored, i.e. "canucks" is equivalent to "Canucks" and "CANUCKS".

## Check NHL game scores with `scores()`
The function `scores()` returns all the NHL game scores from a specified date. `scores()` only takes one argument, a date represented as "YYYY-MM-DD". 

When there is at least one game on the specified date, the output of `scores()` is a dataframe with four variables: 

1. `home`: team common name
2. `away`: away team common name
3. `home_score`: home team score
4. `away_score`: away team score

For example, to see the result of all games on Nov 9th 2014:

```{r}
scores(date = "2014-11-09")
```

Sve
