---
title: "Overview of gameday"
author: "Rebecca Johnston"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of gameday}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## Introduction to gameday

When living in Canada, you must:

* Live hockey;
* Breathe hockey;
* Think about hockey all the time;

Or:
 
* Be banished from civilization and inevitably perish in the tundra.

The `gameday` package helps you to:
 
* Prevent your banishment by providing basic National Hockey League information from live.nhle.com so you can masquerade as a hockey lover.

The `gameday` package has two functions:

1. `gday()`
2. `scores()`

```{r, include=FALSE}
# install_github("rebjoh/gameday")
library("gameday")
```

## Check gameday of a team with `gday()`
The function `gday()` returns TRUE if a specified NHL team plays on a specified date and FALSE otherwise. The first argument is the name of an NHL team (as a chracter string, i.e. team name in quotes), and the second argument is the date of the game, as "YYYY-MM-DD".

For example, to check if the Toronto Maple Leafs played on 9th November 2014 using `gday()`:

```{r, results='hide'}
gday(team = "Maple Leafs", date = "2014-11-09")
```

Or simply:

```{r}
gday("Maple Leafs", "2014-11-09")
```

If no arguments are specified in `gday()`, the default `team` is "Canucks" and the default `date` is today's date. Also note, the case in argument `team` is ignored. Thus the following queries are equivalent:

```{r, results='hide'}
gday()
gday("canucks")
gday("Canucks")
gday("CANUCKS")
```

## Check NHL game scores with `scores()`
The function `scores()` returns all the NHL game scores from a specified date. `scores()` takes one argument, a date represented as "YYYY-MM-DD". When there is at least one game on the date specified, the output of `scores()` is a dataframe with four variable columns: 

1. `home`: team common name
2. `away`: away team common name
3. `home_score`: home team score
4. `away_score`: away team score
5. `game_status`: game status? 1 = scheduled, 3 = in progress, 5 = finished 

For example, to see the result of all NHL hockey games on 9th November 2014:

```{r, results='hide'}
scores(date = "2014-11-09")
```

Or simply:

```{r}
scores("2014-11-09")
```

It is also possible to save the dataframe output to a variable, and perform some data manipulations using `tidyr`, `plyr` and `dplyr` to put the data into tall format:

```{r, warning=FALSE, message=FALSE}
library("tidyr")
library("plyr")
library("dplyr")
library("RColorBrewer")
library("ggplot2")
```

```{r, tidy=FALSE}
scores_2014_11_09 <- scores("2014-11-09")

# Add a new column for game number
scores_2014_11_09 <- 
	mutate(scores_2014_11_09, game_number = as.factor(c(paste("Game", LETTERS[1:nrow(scores_2014_11_09)]))))

# Save home team, home score and game number
scores_2014_11_09_home <- scores_2014_11_09 %>%
	select(home, home_score, game_number) %>%
	plyr::rename(c("home" = "team_name", "home_score" = "score"))

# Save away team, away score and game number
scores_2014_11_09_away <- scores_2014_11_09 %>%
	select(away, away_score, game_number) %>%
	plyr::rename(c("away" = "team_name", "away_score" = "score"))

# Row bind scores_2014_11_09_home and scores_2014_11_09_away
scores_2014_11_09_tall <- rbind(scores_2014_11_09_home, scores_2014_11_09_away)
str(scores_2014_11_09_tall)
(arrange(scores_2014_11_09_tall, game_number))
```

Now the data is in tall format, we can plot the results from each game using `ggplot2`:
```{r ggplot_scores_2014_11_09, fig.width=7, fig.height=6}
colour_pal <- brewer.pal(n = 5, name = "Dark2")
scores_2014_11_09_tall %>%
	ggplot(aes(x = reorder(team_name, desc(score)), y = score, 
						 fill = game_number)) +		 	
	geom_bar(stat = "identity") +
	facet_wrap(~ game_number, scales = "free_x", ncol = 5) +
	theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
	ggtitle("NHL scores from 9th November 2014") +
	ylab("Final score") +
	xlab("Team") +
	theme(legend.position = "none") +
	geom_text(aes(label = score), vjust = 1.5, colour = "white") +
	scale_fill_manual(values = colour_pal)
```
